REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-12-20 main.tex
Update on Overleaf.

We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and static background dark matter potential. The collisionless star particles are evolved with a particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

@@

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range. (\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})

@@

Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$). No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.

We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations. Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$. We complement these tables with tables from Slemer et. al. (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore supernova yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can follow an arbitrary number of metal species, practical considerations 
%mm 
   of memory use 
prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae. Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass 
%mm
    are assumed to
eject their stellar yields via 
%mm ``massive" 
   line-driven
stellar winds at a constant mass loss rate throughout their lifetime
%mm ,
  (neglecting Wolf-Rayet and luminous blue variable phases),
ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.

There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}. Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}. Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no 
%mm
    further
mass or energy ejection.

Type Ia supernovae are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}. 
%mm
    We emphasize that we only track Type Ia supernovae occurring within the 
    population of stars formed in this model, neglecting supernovae from any 
    pre-existing population.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback. 
%mm For both AGB winds and massive stellar winds
    In models that include feedback energy from stellar winds from both AGB and 
    massive stars, 
we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy. The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$. We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
We assume constant mass loss rates for all winds as set by the yields tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.

@@

\subsubsection{Core Collapse Supernovae}
\label{sec: core collapse}
Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse supernovae, ejecting mass and yields as determined by the NuGrid stellar yield tables at 10$^{51}$ erg of thermal energy. Due to the high resolution (1.5--2.5 pc depending on galaxy size) of our simulations, we generally resolve the Sedov phase of each supernova explosion well (see Appendix~\ref{appendix:supernova}). We find injecting thermal energy alone in a three-cell radius spherical region around the star particle to be sufficient to resolve the supernova explosions. We continue to track any remaining stellar mass after the supernovae as a massive ``remnant" tracer particle. In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution.
\textbf{Should I reference a few recent hydro sims that included these feedback sources? - AE  
%mm
Can't hurt if they are ready to hand. Not high priority, though. M-M}

\subsubsection{Type Ia Supernova}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors. At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
%or, 
%\[
%M_{\rm WD} = 
%\begin{cases}
%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
%\end{cases}
%\]
%where $M_{\rm *}$ is the initial mass of the WD progenitor.
We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.

We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. 
%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope and normalization are observables, and $\eta$ the fraction of stars which can form SN Ia progenitors that \textit{will} explode as a SN Ia within a Hubble time. The value for $\eta$ depends on the normalization of the DTD (an observable), as well as one's choice of IMF and mass range of potential SN Ia progenitors (as given above). This fraction is given as
\begin{equation}
\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
\end{equation}
where $N_{\rm Ia}/M_{\rm SF}$ is the DTD normalization, which represents the fraction of stars that form SN Ia progenitors, $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates. The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review). $N_{\rm Ia}/M_{\rm SF}$ represents the number of SN Ia per mass of star formation; this can be derived by taking observed values of the SNIa rate and integrating over a Hubble time. Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}. We adopt 1.2 \citep{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$. Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.

Finally, the probability a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor is taken as

\begin{equation}
P(t) = \dot{P}(t)dt = \eta \frac{ t^{-\beta}}{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau} dt,
\end{equation}

where $t_{\rm o}$ is the formation time of the WD and the denominator normalizes the total probability to $\eta$. This naturally accounts for both a prompt and delayed Type Ia supernova population in our simulations.
In practice, we invert the cumulative probability distribution to assign an exact time at which a given WD will explode, rather than making a random number draw for every WD particle every time step as $\eta$ is small.

\subsubsection{Ionizing Radiation}
\label{sec:ionizing radiation}
Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of pre-SN feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance. However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below. 
%mm In this particular work, we 
  We here
use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).

>>>>

We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}. Self-gravity is computed with a multigrid Poisson solver. The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

@@

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range. %(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})

@@

As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively \textbf{justify choices}. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$). No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.

We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that participate in some way to feedback and metal enrichment, and follow longer lived start particles, while reducing the computational expense of following many low mass stars that have no dynamical impact on the galaxy evolution. 100 M$_{\odot}$ is a reasonable upper limit on the most massive star \textbf{sounds weak}.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a \textbf{1~km~s$^{-1}$ velocity dispersion - justify!}. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations. Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$. We complement these tables with tables from Slemer et. al. (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore supernova yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae. Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.

There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}. Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}. Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass or energy ejection.

Type Ia supernovae are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}. We emphasize that we only track Type Ia supernovae occurring within the population of stars formed in this model, neglecting supernovae from any pre-existing population.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback. In models that include feedback energy from stellar winds from both AGB and  massive stars, we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy. The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$. We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.

We assume constant mass loss rates for all winds as set by the yields tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.

@@

\subsubsection{Core Collapse Supernovae}
\label{sec: core collapse}
Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse supernovae, ejecting mass and yields as determined by the NuGrid stellar yield tables at 10$^{51}$ erg of thermal energy. Due to the high resolution (1.5--2.5 pc depending on galaxy size) of our simulations, we generally resolve the Sedov phase of each supernova explosion well (see Appendix~\ref{appendix:supernova}). We find injecting thermal energy alone in a three-cell radius spherical region around the star particle to be sufficient to resolve the supernova explosions. We continue to track any remaining stellar mass after the supernovae as a massive ``remnant" tracer particle. In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution \citep[e.x.][]{Artale2015}.

\subsubsection{Type Ia Supernova}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors. \textbf{This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations. (worth mentioning? maybe softer version of this?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time. For example, by the end of the simulation presented here (XXX Myr), only XXX have gone off. At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
%or, 
%\[
%M_{\rm WD} = 
%\begin{cases}
%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
%\end{cases}
%\]
%where $M_{\rm *}$ is the initial mass of the WD progenitor.
We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.

We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. 
%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope ($\beta$) and normalization ($N_{\rm 1a}/M_{\rm SF}$) are observables. The latter represents the number of Type 1a supernova per mass of star formation. By assuming an IMF, one can write down the fraction ($\eta$) of stars capable of forming a SNIa progenitor that \textit{will} explode within a Hubble time. This is given as
\begin{equation}
\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
\end{equation}
where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates. The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review). $N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the SNIa rate and integrating over a Hubble time. Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}. We adopt 1.2 \citep{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$. Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.

Finally, we can normalize $\Psi(t)$ to give the probability per unit time ($\dot{P}(t)$) that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor. Integrating this gives the total probability at any given time as,

\begin{equation}
P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
\end{equation}
where $t_{\rm o}$ is the formation time of the WD and the leading term in the R.H.S properly normalizes the total probability over a Hubble time to $\eta$. This naturally accounts for both a prompt and delayed Type Ia supernova population in our simulations.
In practice, we invert the cumulative probability function to assign an exact time at which a given WD will explode using only a single random number draw, rather than sampling the probability distribution for each WD particle at every time step.

\subsubsection{Ionizing Radiation from Discrete Sources}
\label{sec:ionizing radiation}
Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance. However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below. 
% AE (no longer the case): We here use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
